Classification of massless supermultiplets

### 2020-02-24 old stuff/4dsusy.tex
reorganize

\begin{lem}
\label{lem: oneform}
Let $\alpha$ be any $1$-form on $V$, $\psi \in C^\infty(V, \Sigma)$,  and $Q \in \Sigma$. 
Then
\[
\d (Q, \psi) \wedge * \alpha = * (\rho(\alpha)Q, \sd \dd \psi) .
\]
\end{lem}
\begin{proof}
Let $V_\alpha$ denote the vector field corresponding to $\alpha$. 
Note that $\d(Q,\psi) \wedge * \alpha = * (Q, V_\alpha . \psi)$. 
The result then follows from invariance of $(-,-)$ and the formula $\sd \dd \psi = \rho(\d x_i) (\partial_i \psi)$. 
\end{proof}

@@

The action of the odd part of the $4d$ $\cN=1$ supersymmetry algebra on the $4$-dimensional matter theory is encoded by the following linear and quadratic functionals 
\begin{align*}
I^{(1)}(Q) & = \int \<\phi^*, (Q, \psi_+)\>_R + \<\Bar{\phi}^*, (Q, \psi_-)\>_R + \<\psi_+^*, \rho(\d \phi)Q \>_R +  \<\psi_-^*, \rho(\d \Bar{\phi})Q \>_R \\
I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^*, \psi_-^*)) - (Q_1, \psi_+^*)(Q_2, \psi_-^*) - \int (Q_2, \psi_+^*)(Q_1, \psi_-^*) 
\end{align*}
for $Q, Q_1, Q_2 \in S_+ \oplus S_-$

@@

\begin{lemma} 
One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in S_+ + S_-$. 
\end{lemma}
\begin{proof}
The BV bracket involving terms in $S$ depending on $\phi,\Bar{\phi}$ is:
\begin{align*}
- \left\{\d \phi \wedge * \d \Bar{\phi} \; , \; I^{(1)} \right\}  (Q) & = \d (Q, \psi_+) \wedge * \d \Bar{\phi} + \d \phi \wedge * \d (Q_-, \psi_-) 
%\\
%& = \Gamma(\sd \dd \psi_+, Q) \wedge * \d \Bar{\phi} \pm \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q_-) .
\end{align*}
The BV bracket involving terms in $S$ depending on $\psi_\pm$ is:
\begin{align*}
\left\{ (\psi_+ , \sd \dd \psi_-) \; , \; I^{(1)} \right\} (Q) & = (\rho(\d \phi) Q, \sd \dd \psi_-) + (\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q)) \\ & =  (\rho(\d \phi) Q, \sd \dd \psi_-) - (\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q) \\ & = \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q) - \d \Bar{\phi} \wedge * \Gamma(\sd \dd \psi_+, Q)
\end{align*}
Adding the two terms up, we see that $\{S,I^{(1)}\}(Q) = 0$ by Lemma \ref{lem: oneform} as desired. 
\end{proof}

@@

and
\begin{align*}
\{S, I^{(2)}(Q_1,Q_2)\} = & 
\end{align*}

We first collect all terms in Equation (\ref{CMEchiral3}) proportional to $\phi^*$:
\[
- \frac{1}{2} (Q_1, \rho(\d\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d \phi) Q_1) - L_{\Gamma(Q_1,Q_2)} \phi .
\]
By Proposition \ref{??}
\brian{ $v \wedge \Gamma(Q_1, Q_2) = (Q_1 , \rho(v) Q_2)$} we observe that the first two terms cancel with the third term. 
Similarly, all terms proportional to $\Bar{\phi}^*$ also vanish.

Next, we collect all terms in Equation (\ref{CMEchiral3}) proportional to $\psi_+^*$:
\begin{align*}
& - \frac{1}{2} \rho(\d(Q_1,\psi_+))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi_+)) Q_1 - \Gamma(Q_1,Q_2) . \psi_+
\\ 
& \pm \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi_+ \mp \frac{1}{2} (Q_2, \sd \dd \psi_+)Q_1 \mp \frac{1}{2} (Q_1, \sd \dd \psi_+)Q_2
\end{align*}

\end{proof}

@@

Next, we move on to the pure gauge sector $\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I^{(1)}_{\rm gauge} + I^{(2)}_{\rm gauge}$. 
\end{proof}

>>>>

\begin{lem}
\label{lem: oneform}
Let $v \in V$, $\psi \in C^\infty(V, \Sigma)$, and $Q \in \Sigma$. 
Then
\[
(v, \d (Q, \psi))_V = (\rho(v)Q, \sd \dd \psi)_{\Sigma} .
\]
\end{lem}
\begin{proof}
Let $V_\alpha$ denote the vector field corresponding to $\alpha$. 
Note that $\d(Q,\psi) \wedge * \alpha = * (Q, V_\alpha . \psi)$. 
The result then follows from invariance of $(-,-)$ and the formula $\sd \dd \psi = \rho(\d x_i) (\partial_i \psi)$. 
\end{proof}

\begin{lem}
\label{lem: silly}
For $Q_1,Q_2 \in \Sigma$ and $\psi_+ \in S_+$ we have
\[
\rho(\d(Q_1, \psi_+)) Q_2 = \rho(\Gamma(Q_1, \sd \dd \psi_+))Q_2
\]
\end{lem}

\brian{I'd also  like the following  to be true.
\begin{prop}
Suppose $Q_+ \in S_+$, $Q_-\in S_-$, and $\psi_+ \in C^\infty(V , S_+)$. 
Then
\[
\sd \dd (\rho(\Gamma(Q_+, Q_-)) \psi_+) = \rho(\d(Q_+, \psi_+)) Q_- + (Q_-, \sd \dd \psi_+)Q_+ .
\]
\end{prop}
}

@@

The action of the odd part of the $4d$ $\cN=1$ supersymmetry algebra on the $4$-dimensional matter theory is encoded by the following linear and quadratic functionals 
\begin{align*}
I^{(1)}(Q) & = \int \<\phi^*, (Q, \psi_+)\>_R + \<\Bar{\phi}^*, (Q, \psi_-)\>_R + \<\psi_+^*, \rho(\d \phi)Q \>_R +  \<\psi_-^*, \rho(\d \Bar{\phi})Q \>_R \\
I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^*, \psi_-^*)_R) - ((Q_1, \psi_+^*),(Q_2, \psi_-^*))_R - ((Q_2, \psi_+^*),(Q_1, \psi_-^*))_R
\end{align*}
for $Q, Q_1, Q_2 \in S_+ \oplus S_-$
A word on the notation used in the definition of $I^{(2)}$. 
The $V$-valued pairing $\Gamma(\psi_+^*, \psi_-^*)_R$ denotes the image of $\psi_+^* \otimes \psi_-^*$ under the composition
\[
(S_+ \otimes R^*) \otimes (S_- \otimes R) \cong (S_+ \otimes S_-) \otimes (R^* \otimes R) \xto{\Gamma \otimes (-,-)_R} V .
\]
Additionally, we view $(Q_1, \psi_+^*)$ as a scalar valued in $R^*$ and $(Q_2, \psi_-^*)$ as a scalar valued in $R$. 
The pairing $((Q_1, \psi_+^*),(Q_2, \psi_-^*))_R$ is the obvious one between $R$ and $R^*$.

@@

\begin{lemma} 
One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in S_+ + S_-$. 
\end{lemma}
\begin{proof}
The BV bracket involving terms in $S$ depending on $\phi,\Bar{\phi}$ is:
\begin{align*}
- \left\{(\d \phi, \d \Bar{\phi}) \; , \; I^{(1)} \right\}  (Q) & = (\d (Q, \psi_+), \d \Bar{\phi}) + (\d \phi, \d (Q_-, \psi_-))
%\\
%& = \Gamma(\sd \dd \psi_+, Q) \wedge * \d \Bar{\phi} \pm \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q_-) .
\end{align*}
The BV bracket involving terms in $S$ depending on $\psi_\pm$ is:
\begin{align*}
\left\{ (\psi_+ , \sd \dd \psi_-) \; , \; I^{(1)} \right\} (Q) & = (\rho(\d \phi) Q, \sd \dd \psi_-) + (\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q)) \\ & =  (\rho(\d \phi) Q, \sd \dd \psi_-) - (\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q) \\ & =( \d \phi , \Gamma(\sd \dd \psi_-, Q)) - (\d \Bar{\phi} , \Gamma(\sd \dd \psi_+, Q))
\end{align*}
Adding the two terms up, we see that $\{S,I^{(1)}\}(Q) = 0$ by Lemma \ref{lem: oneform} as desired. 
\end{proof}

@@

and
\begin{align*}
\{S, I^{(2)}(Q_1,Q_2)\} = \left\{(\psi_+ , \sd \dd \psi_-), I^{(2)} \right\} = & \Gamma(Q_1,Q_2) \Gamma(\psi_+^*, \sd \dd \psi_+) - (Q_1 , \psi_+^*)(Q_2, \sd \dd \psi_+) - (Q_2, \psi_+^*)(Q_1, \sd\dd \psi_+)  \\ 
 + & \Gamma(Q_1, Q_2) \Gamma(\psi_-^*, \sd \dd \psi_-) - (Q_1 , \psi_-^*)(Q_2, \sd \dd \psi_-) - (Q_2, \psi_-^*)(Q_1, \sd\dd \psi_-) \\
 = & (\psi_+^*, \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi_+) - (Q_1 , \psi_+^*)(Q_2, \sd \dd \psi_+) - (Q_2, \psi_+^*)(Q_1, \sd\dd \psi_+) \\ 
 + & (\psi_-^*, \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi_-) - (Q_1 , \psi_-^*)(Q_2, \sd \dd \psi_-) - (Q_2, \psi_-^*)(Q_1, \sd\dd \psi_-) .
\end{align*}

We first collect all terms in Equation (\ref{CMEchiral3}) proportional to $\phi^*$:
\[
- \frac{1}{2} (Q_1, \rho(\d\phi) Q_2) - \frac{1}{2} (Q_2, \rho(\d \phi) Q_1) - L_{\Gamma(Q_1,Q_2)} \phi .
\]
By the Clifford identity
\brian{ $v \wedge \Gamma(Q_1, Q_2) = (Q_1 , \rho(v) Q_2)$} we observe that the first two terms cancel with the third term. 
Similarly, all terms proportional to $\Bar{\phi}^*$ also vanish.

Next, we collect all terms in Equation (\ref{CMEchiral3}) proportional to $\psi_+^*$:
\begin{align*}
& - \frac{1}{2} \rho(\d(Q_1,\psi_+))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi_+)) Q_1 - \Gamma(Q_1,Q_2) . \psi_+
\\ 
& \pm \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi_+ \mp \frac{1}{2} (Q_2, \sd \dd \psi_+)Q_1 \mp \frac{1}{2} (Q_1, \sd \dd \psi_+)Q_2
\end{align*}
By Lemma \ref{lem: silly} the first, second terms, and fourth terms are equal to 
\[
-\frac{1}{2}   \rho(\Gamma(Q_1, \sd \dd \psi_+))Q_2 - \frac{1}{2}   \rho(\Gamma(Q_2, \sd \dd \psi_+))Q_1 + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi_+
\]
This is zero by Proposition \brian{3-psi}.

The remaining terms are
\[
- \Gamma(Q_1,Q_2) . \psi_+ + \frac{1}{2} (Q_2, \sd \dd \psi_+)Q_1 + \frac{1}{2} (Q_1, \sd \dd \psi_+)Q_2 .
\]
\end{proof}

@@

Next, we move on to the pure gauge sector $\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I^{(1)}_{\rm gauge} + I^{(2)}_{\rm gauge}$. 
\end{proof}
1405.99

387.00
318.99

### 2020-02-24 old stuff/matter.tex
reorganize

@@

\begin{itemize}
\item[(1)] Dimension $n = 4$.
Suppose $Q_+ \oplus Q_- \in S_+ \oplus S_-$.
Then, the following diagram commutes
\[
\xymatrix{
S_+ \otimes S_- \ar[dr]_-{(Q_+ + Q_-,-)} \ar[rr]^-{\Gamma} & & V \ar[dl]^-{\rho(v)} \\
& S_+ \oplus S_- &  
}
\]
\item[(2)] Dimension $n = 6$. 
Suppose $Q \in S_\mp$.
Then, the following diagram commutes
\[
\xymatrix{
\wedge^2 S_\pm \ar[dr]_-{(Q,-)} \ar[rr]^-{\Gamma} & & V \ar[dl]^-{\rho(v)} \\
& S_\pm & 
}
\]
\end{itemize}
\end{prop}

To a supersymmetric matter pair we will associate a free BV theory whose underlying BRST fields consist of:
\begin{itemize}
\item a scalar $\phi \in C^\infty(\RR^n ; \SS^*)$;
\item a negative Weyl spinor valued in $U$; $\psi \in C^\infty(\RR^4 ; S_- \otimes U)$ .
\begin{dfn}
The BRST theory associated to a supersymmetric matter pair (even or odd) $(\SS, U)$ has underlying bundle of BRST fields:
\[

>>>>

\brian{Not sure if this is the correct formulation. The matter and fermions are treated differently in a theory of matter.}

@@

\begin{itemize}
\item[(1)] Dimension $n = 4$.
Suppose $Q_+ + Q_- \in S_+ \oplus S_-$.
Then, the following diagram commutes
\[
\xymatrix{
S_+ \otimes S_- \ar[dr]_-{(Q_+ + Q_-,-)} \ar[rr]^-{\Gamma} & & V \ar[dl]^-{\rho(-)(Q_+ + Q_-)} \\
& S_+ \oplus S_- &  
}
\]
\item[(2)] Dimension $n = 6$. 
Suppose $Q \in S_\mp$.
Then, the following diagram commutes
\[
\xymatrix{
\wedge^2 S_\pm \ar[dr]_-{(Q,-)} \ar[rr]^-{\Gamma} & & V \ar[dl]^-{\rho(-)Q} \\
& S_\pm & 
}
\]
\end{itemize}
\end{prop}

To a supersymmetric matter pair we will associate a free BV theory whose underlying BRST fields consist of:
\begin{itemize}
\item a scalar $\phi \in C^\infty(\RR^n ; \SS^*)$;
\item a negative Weyl spinor valued in $U$; $\psi \in C^\infty(\RR^4 ; S_- \otimes U)$ .
\end{itemize}

\begin{definition}
The BRST theory associated to a supersymmetric matter pair (even or odd) $(\SS, U)$ has underlying bundle of BRST fields:
\end{definition}

### 2020-02-24 old stuff/supermultiplets.tex
reorganize

Let $V$ be a complex vector space with a chosen spin structure. Let $\Sigma$ be a spinorial representation of $\Spin(V)$, $\Gamma\colon \Sym^2(\Sigma)\rightarrow V$ the associated vector-valued pairing and $T_\Sigma$ the supertranslation group with Lie algebra $\Pi\Sigma\oplus V$. The superPoincar\'{e} group is $\Spin(V)\ltimes T_\Sigma$.

Recall that massless representations of the Poincar\'{e} group are parametrized in the following way. Split $V = V_0\oplus \C e_+\oplus \C e_-$, where $e_+$ and $e_-$ are null vectors with $(e_+, e_-) = 1$. Then massless representations correspond to finite-dimensional representations of $\Spin(V_0)$.

>>>>

Let $V$ be a complex vector space of dimension $d$ with a chosen spin structure. Let $\Sigma$ be a spinorial representation of $\Spin(V)$, $\Gamma\colon \Sym^2(\Sigma)\rightarrow V$ the associated vector-valued pairing, and $T_\Sigma$ the supertranslation group with Lie algebra $\Pi\Sigma\oplus V$. The superPoincar\'{e} group is the semi-direct product $\Spin(V)\ltimes T_\Sigma$.

Recall that massless representations of the Poincar\'{e} group are parametrized in the following way. Split $V = V_0\oplus \C e_+\oplus \C e_-$, where $e_+$ and $e_-$ are null vectors satisfying $(e_+, e_-) = 1$. Then massless representations correspond to finite-dimensional representations of $\Spin(V_0)$.
